---
title: "Process Book"
author: "Sunny Mahesh"
author: "Eliana Marostica"
author: "Maria Nakhoul"
date: "4/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Team Members
#### 4/4/19

Sunny Mahesh, Eliana Marostica, and Maria Nakhoul

## Data Set
#### 4/11/19

We will be using 3 data sets freely available online from the CDC

```{r load}
setwd("../")
iddr <- read_csv("data/Impaired_Driving_Death_Rate__by_Age_and_Gender__2012___2014__All_States.csv")
ocdr <- read_csv("data/Motor_Vehicle_Occupant_Death_Rate__by_Age_and_Gender__2012___2014__All_States.csv")
sebt <- read_csv("data/Percentage_of_Drivers_and_Front_Seat_Passengers_Wearing_Seat_Belts__2012___2014__All_States.csv")
```

#### Impaired Driving Death Rates by Age and Gender (2012 & 2014)

```{r}
iddr %>%
  summary()
```

#### Motor Vehicle Occupant Death Rates by Age and Gender (2012 & 2014)

```{r}
ocdr %>%
  summary()
```


There are two time points for the OCDR data 2012 and 2014. There are 2 main attributes sex and age. There are 52 elements (50 states, DC, and USA as a whole). All of the data is numeric data, where the values are the number of deaths for that specific category.

#### Percentage of Drivers and Front Seat PAssengers Wearing Seat Belts

```{r}
sebt %>%
  summary()
```

```{r}
indicies_max_2012<-which(sebt$`2012`==max(sebt$`2012`))
sebt[indicies_max_2012,]
indicies_min_2012<-which(sebt$`2012`==min(sebt$`2012`))
sebt[indicies_min_2012,]
indicies_max_2014<-which(sebt$`2014`==max(sebt$`2014`))
sebt[indicies_max_2014,]
indicies_min_2014<-which(sebt$`2014`==min(sebt$`2014`))
sebt[indicies_min_2014,]
```

In 2012, the state with the maximum number of drivers and front seat passangers wearing a seat belt are Washington and Oregon, while the state with the minimum number is South Dakota.


In 2014, the state with the maximum number of drivers and front seat passangers wearing a seat belt is Oregon, while the state with the minimum number is South Dakota.
## Visualization Tasks and Requirements
#### 4/18/19


