---
title: "Process Book"
author: "Sunny Mahesh"
author: "Eliana Marostica"
author: "Maria Nakhoul"
date: "4/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Team Members
#### 4/4/19

Sunny Mahesh, Eliana Marostica, and Maria Nakhoul

## Data Set
#### 4/11/19

We will be using 3 data sets freely available online from the CDC

```{r load}
setwd("../")
iddr <- read_csv("data/Impaired_Driving_Death_Rate__by_Age_and_Gender__2012___2014__All_States.csv")
ocdr <- read_csv("data/Motor_Vehicle_Occupant_Death_Rate__by_Age_and_Gender__2012___2014__All_States.csv")
sebt <- read_csv("data/Percentage_of_Drivers_and_Front_Seat_Passengers_Wearing_Seat_Belts__2012___2014__All_States.csv")
```

#### Impaired Driving Death Rates by Age and Gender (2012 & 2014)

Summarize the variables, data types (temporal, networks, multivariate matrices, etc.),
and key statistics (# of elements, # of attributes, # of timepoints, etc.) of your data set.

The key variables here are state, location (of the state), age group (all,0-20, 21-34, 35+), year (2012,2014), sex, and death rate. The data type here is numeric - these are death rates. There are two timepoints: 2012 and 2014. These death rates are available for each of the 50 states plus Washington D.C. and the United Sates as a whole.


```{r}
iddr %>%
  summary()
```




#### Motor Vehicle Occupant Death Rates by Age and Gender (2012 & 2014)

```{r}
ocdr %>%
  summary()
```

#### Percentage of Drivers and Front Seat PAssengers Wearing Seat Belts

```{r}
sebt %>%
  summary()
```

## Visualization Tasks and Requirements
#### 4/18/19


